---
title: "Schedule"
page-layout: full
css: layout/css/econpol.scss
---

```{r packages, include=FALSE, cache=FALSE}
library(tidyverse)
library(readxl)
library(glue)
library(knitr)
library(kableExtra)

Sys.setlocale(locale="en_US.UTF-8")
schedule <- read_xlsx(here::here("data/schedule/schedule.xlsx"))
```

In this table you find the dates and contents of all classes.


::: {.schedule-table}
```{r table, echo=F, results='asis'}
schedule %>% arrange(Date) %>% select(-c(Paper,PDF)) %>%
  mutate(Slides = ifelse(!is.na(Slides),
        glue('<a href="slides/{Slides}/" target = "_blank">
             <i class="fa-solid fa-display fa-lg"></i></a>'),
        glue('<font color="#e9ecef"><i class="fa-solid fa-display fa-lg"></i></font>')), 
        Assignment = ifelse(!is.na(Assignment),
        glue('<a href="#h{Assignment}"><i class="fa-solid fa-pen fa-lg"></i></a>'),
        glue('<font color="#e9ecef"><i class="fa-solid fa-pen fa-lg"></i></font>')),
        Date = format(Date, '%b %d, %Y')) %>%
  kbl(escape = FALSE, align = "cclcc", table.attr = 'class="schedule-table"') %>% 
  kable_styling() %>% 
  column_spec(1:2, width = "15%") %>% 
  column_spec(3, width = "40%") %>% 
  column_spec(4:6, width = "10%")
```
:::

#### Assignments

While assignments [[1]](#h1) and [[3]](#h3) are mandatory, students may choose between [[2]](#h2) and [[4]](#h4). Please write a concise and consistent summary of the provided paper with a **limit of 400 words** and upload it on the [learning platform](https://learn.wu.ac.at). The submission deadline is **9 a.m. on the day of the respective teaching unit**. You can structure your text around the following questions:

- What is the research question?
- Why is this question interesting?
- How does the author approach and answer this question? 
- What are the main findings? 
- Is the paper credible? Why? Why not?

##### Homework 1{#h1}

```{r assign1, include = F}
assignvars <- schedule %>% filter(!is.na(Assignment)) %>%
  mutate(deadline = format(Date, '%B %d, %Y'),
         citation = paste0("@", Paper),
         pdf = paste0("data/lit/", PDF, ".pdf"))
```

This assignment is mandatory. Please submit your summary before `r assignvars$deadline[[1]]` at 9 a.m. The journal article for this assignment is `r assignvars$citation[[1]]` &nbsp; <a href = "`r assignvars$pdf[[1]]`">{{< fa file-pdf >}}</a>

##### Homework 2{#h2}

This assignment is optional. If you choose not to read this paper, assignment [[4]](#h4) is mandatory. Please submit your summary before `r assignvars$deadline[[2]]` at 9 a.m. The journal article for this assignment is `r assignvars$citation[[2]]` &nbsp; <a href = "`r assignvars$pdf[[2]]`">{{< fa file-pdf >}}</a>

##### Homework 3{#h3}

This assignment is mandatory. Please submit your summary before `r assignvars$deadline[[3]]` at 9 a.m. The journal article for this assignment is `r assignvars$citation[[3]]` &nbsp; <a href = "`r assignvars$pdf[[3]]`">{{< fa file-pdf >}}</a>

##### Homework 4{#h4}

This assignment is optional. If you choose not to read this paper, assignment [[2]](#h2) is mandatory. Please submit your summary before `r assignvars$deadline[[4]]` at 9 a.m. The journal article for this assignment is `r assignvars$citation[[4]]` &nbsp; <a href = "`r assignvars$pdf[[4]]`">{{< fa file-pdf >}}</a>